---
title: "Statistical Analysis Pipeline"
subtitle: "Experiments 1, 2, & 3 (Representational Momentum)"
author: "Analysis Pipeline"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    theme: united
    code_folding: show
---

```{r setup, include=FALSE}
# This setting ensures code displays on GitHub without requiring raw data files.
# The logic is preserved for examiner inspection.
knitr::opts_chunk$set(eval = FALSE, echo = TRUE, message = FALSE, warning = FALSE, fig.width = 10, fig.height = 8)

library(tidyverse)
library(afex)
library(emmeans)
library(lme4)
library(lmerTest)
library(DHARMa)
library(knitr)
library(patchwork)
library(gridExtra)

# Set Sums of Squares to Type 3 
afex_options(type = 3)
```

# Data Loading & Cleaning 

```{r load, echo=FALSE}
# This pipeline is identical for Exp 1 (Horizontal), Exp 2 (Upward), and Exp 3 (Downward). It was run individually, each in a different rmd file. The below repre

# Data paths are generic.
# file_path <- "data/raw_data/experiment_1_horizontal.csv"
# file_path <- "data/raw_data/experiment_2_upward.csv"
# file_path <- "data/raw_data/experiment_3_downward.csv"


rm1_raw <- read_csv(filename_RM1, col_types = cols(
  errorFwd_px = col_character(),
  fileID      = col_character()
))

# Initial formatting & Normalization 
# Normalize case to prevent data loss (NAs)
df_initial_RM1 <- rm1_raw %>%
  rename(participant_id = fileID) %>%
  mutate(
    errorFwd_px_num = as.numeric(errorFwd_px),
    direction       = as.numeric(direction), 
    pathGeometry    = factor(tolower(trimws(pathGeometry)), levels = c("linear", "sinusoidal")),
    pathVisible     = factor(tolower(trimws(pathVisible)),  levels = c("invisible", "visible"))
  )

# Critical Factor Check
if(any(is.na(df_initial_RM1$pathGeometry)) || any(is.na(df_initial_RM1$pathVisible))) {
  stop("CRITICAL ERROR: Unexpected factor levels in raw data (produced NAs). Check spelling/capitalization.")
}

# Calculate Trial Issues 
df_initial_filtered <- df_initial_RM1 %>%
  filter(!is.na(errorFwd_px_num)) %>%
  select(participant_id, trial, pathGeometry, pathVisible, direction, 
         errorFwd_px_num, errorOrth_px, 
         clickX_px, clickY_px, vanishX_px, vanishY_px)

issues_RM1 <- rm1_raw %>%
   group_by(fileID) %>%
  summarise(
    n_trials  = n(),
    n_missing = length(setdiff(1:80, sort(unique(trial)))), 
    .groups = "drop"
  )

# SURGICAL FILTER: Remove participants with > 5 missing trials
MISSING_THRESHOLD <- 5 

participants_to_drop <- issues_RM1 %>%
  filter(n_missing > MISSING_THRESHOLD) %>%
  pull(fileID)

cat("\n--- Data Integrity Check ---\n")
if(length(participants_to_drop) > 0) {
  cat("DROPPING participants (> ", MISSING_THRESHOLD, " missing trials):\n")
  cat(paste(participants_to_drop, collapse=", "), "\n")
} else {
  cat("No participants dropped (all within missing trial limit).\n")
}

df_initial <- df_initial_filtered %>%
  filter(!participant_id %in% participants_to_drop)

cat("\nFinal Valid N (Participants):", length(unique(df_initial$participant_id)), "\n")
cat("Final Valid N (Trials):", nrow(df_initial), "\n")
```

# Step 1: Two-Step Data Filtering
## Criteria: 1. Remove "Crazy Clicks" (>100px absolute error). 2. Remove trials > 2.5 SDs from the individual's mean.

```{r two_step_filtering, echo=FALSE}
# Absolute Cutoff 
abs_cutoff <- 100
df_step1_abs <- df_initial %>%
  filter(abs(errorOrth_px) <= abs_cutoff & abs(errorFwd_px_num) <= abs_cutoff)

n_crazy <- nrow(df_initial) - nrow(df_step1_abs)

# Statistical Filtering (Individual SD)
df_step1_calc <- df_step1_abs %>%
  group_by(participant_id) %>%
  mutate(
    indiv_mean = mean(errorFwd_px_num, na.rm = TRUE),
    indiv_sd   = sd(errorFwd_px_num, na.rm = TRUE),
    lower_limit = indiv_mean - (2.5 * indiv_sd),
    upper_limit = indiv_mean + (2.5 * indiv_sd),
    is_trial_outlier = errorFwd_px_num < lower_limit | errorFwd_px_num > upper_limit
  ) %>%
  ungroup()

df_clean_trials <- df_step1_calc %>%
  filter(!is_trial_outlier)

n_sd_removed <- nrow(df_step1_abs) - nrow(df_clean_trials)

print(paste("--- Step 1 Report ---"))
print(paste("Original Count:", nrow(df_initial)))
print(paste("Crazy Clicks Removed (>100px):", n_crazy))
print(paste("Statistical Outliers Removed (>2.5 Indiv SD):", n_sd_removed))
print(paste("Final Clean Trial Count:", nrow(df_clean_trials)))

df_dist_compare <- bind_rows(
  df_initial %>% mutate(Status = "Raw (Pre-filter)"),
  df_clean_trials %>% mutate(Status = "Cleaned (Post-filter)")
)
```

```{r extreme_outliers}
extreme_outliers <- df_dist_compare %>%
  filter(errorFwd_px_num < -200)
print(extreme_outliers)
```

# Quality Control: Pre vs. Post Filtering Analysis

```{r quality_control, echo=FALSE, include=FALSE, fig.width=11, fig.height=5}
# Calculate exclusion rates
exclusion_stats <- df_initial %>%
  group_by(participant_id) %>%
  summarise(n_total = n(), .groups = "drop") %>%
  left_join(
    df_clean_trials %>%
      group_by(participant_id) %>%
      summarise(n_kept = n(), .groups = "drop"),
    by = "participant_id"
  ) %>%
  mutate(
    n_kept      = replace_na(n_kept, 0),
    n_removed  = n_total - n_kept,
    pct_removed = (n_removed / n_total) * 100
  )

exclusion_stats_pretty <- exclusion_stats %>%
  mutate(
    ppt_index = as.numeric(factor(participant_id)),
    ppt_label = factor(paste0("P", ppt_index), levels = paste0("P", sort(unique(ppt_index))))
  )

# Plot: % removed
p_loss <- ggplot(exclusion_stats_pretty, aes(x = ppt_label, y = pct_removed)) +
  geom_col(fill = "#f5e0c7", color = "grey40", width = 0.7) +
  geom_hline(yintercept = 10, linetype = "dashed", color = "grey40") +
  labs(title = "Data Loss by Participant", y = "% Trials Removed", x = NULL) +
  theme_bw(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Distribution plot
p_dist_zoomed <- ggplot(df_dist_compare, aes(x = Status, y = errorFwd_px_num, fill = Status)) +
  geom_boxplot(width = 0.5, outlier.colour = "red", outlier.alpha = 0.5) +
  scale_fill_manual(values = c("Raw (Pre-filter)" = "grey80", "Cleaned (Post-filter)" = "#4575b4")) +
  coord_cartesian(ylim = c(-100, 100)) + 
  labs(title = "Distribution Shift (Zoomed)", y = "Forward Error (px)", fill = NULL) +
  theme_bw(base_size = 12) +
  theme(legend.position = "none")

gridExtra::grid.arrange(p_loss, p_dist_zoomed, ncol = 2)

exclusion_stats %>%
  select(participant_id, n_total, n_removed, pct_removed) %>%
  arrange(desc(pct_removed)) %>%
  kable(digits = 1, caption = "Detailed Exclusion Statistics")
```

## Step 2: Global Participant Check & Final Dataset Creation

```{r validity_check, echo=FALSE}
ppt_summary <- df_clean_trials %>%
  group_by(participant_id) %>%
  summarise(ppt_mean_error = mean(errorFwd_px_num), .groups = "drop")

group_mean <- mean(ppt_summary$ppt_mean_error)
group_sd   <- sd(ppt_summary$ppt_mean_error)

flagged_global <- ppt_summary %>%
  filter(abs(ppt_mean_error - group_mean) > 2.5 * group_sd) %>%
  pull(participant_id)

cat("--- Step 2: Global Outlier Report ---\n")
cat("Group Mean Error:", round(group_mean, 2), "px\n")
cat("Participants Flagged:", length(flagged_global), "\n")

# (Normalization already handled in load_data, but kept here for safety/explicit structure)
df_analysis_A <- df_clean_trials 
df_analysis_B <- df_clean_trials %>% filter(!participant_id %in% flagged_global)

print(paste("Dataset A (Full) Trials:", nrow(df_analysis_A)))
print(paste("Dataset B (Sensitivity) Trials:", nrow(df_analysis_B)))

# ROBUST VALIDATION: HETEROGENEOUS PIXEL RATIOS
df_val <- df_analysis_A %>%
  mutate(
    dist_physical = sqrt((clickX_px - vanishX_px)^2 + (clickY_px - vanishY_px)^2),
    dist_linear_physical = (clickX_px - vanishX_px) * direction
  )

ppt_dpr <- df_val %>%
  filter(pathGeometry == "linear") %>%
  group_by(participant_id) %>%
  summarise(
    dpr_est = coef(lm(dist_linear_physical ~ 0 + errorFwd_px_num))[1],
    r_sq    = summary(lm(dist_linear_physical ~ 0 + errorFwd_px_num))$r.squared,
    .groups = "drop"
  )

print("--- PER-PARTICIPANT INTEGRITY CHECK (DPR Estimation) ---")
print(ppt_dpr)

df_val_checked <- df_val %>%
  left_join(ppt_dpr, by = "participant_id") %>%
  mutate(
    errorFwd_physical_reconstructed = errorFwd_px_num * dpr_est,
    linear_diff = abs(errorFwd_physical_reconstructed - dist_linear_physical),
    is_geom_valid = abs(errorFwd_physical_reconstructed) >= (dist_physical - 2.0)
  )

linear_fail <- df_val_checked %>% filter(pathGeometry == "linear" & linear_diff > 2.0)
sinusoidal_fail <- df_val_checked %>% filter(pathGeometry == "sinusoidal" & !is_geom_valid)

print(paste0("--- FINAL VALIDATION REPORT ---"))
print(paste0("Linear Mismatches (>2px): ", nrow(linear_fail)))
print(paste0("Sinusoidal Geometry Violations: ", nrow(sinusoidal_fail)))

ggplot(df_val_checked %>% filter(pathGeometry == "linear"), 
       aes(x = errorFwd_physical_reconstructed, y = dist_linear_physical)) +
  geom_point(alpha=0.3) +
  geom_abline(color="red", linetype="dashed") +
  labs(title = "Validation: Reconstructed Arc Length vs Physical Geometry",
       x = "Reconstructed Forward Error (Physical px)", y = "Raw Coordinate Distance (Physical px)") +
  theme_bw()
```


# Step 3: Condition-Wise Subject Check 
## Criteria: Detect participants who are extreme outliers (> 2.5 Group SD) in specific conditions only.

```{r step3_cond_check, echo=FALSE}
# Use df_analysis_A to ensure consistency with final analysis set
cond_summary <- df_analysis_A %>%
  group_by(participant_id, pathGeometry, pathVisible) %>%
  summarise(mean_error = mean(errorFwd_px_num), .groups = 'drop')

outliers_cond <- cond_summary %>%
  group_by(pathGeometry, pathVisible) %>%
  mutate(
    group_cond_mean = mean(mean_error),
    group_cond_sd = sd(mean_error),
    z_score = (mean_error - group_cond_mean) / group_cond_sd,
    is_cond_outlier = abs(z_score) > 2.5
  ) %>%
  filter(is_cond_outlier) 

cat("--- Step 3: Condition-Specific Outlier Report ---\n")
if (nrow(outliers_cond) > 0) {
  outliers_cond %>%
    select(participant_id, pathGeometry, pathVisible, mean_error, z_score) %>%
    arrange(participant_id, pathGeometry, pathVisible) %>%
    kable(digits = 2, caption = "Condition-wise outlier participants (|z| > 2.5)")
} else {
  cat("No condition-wise outliers detected.\n")
}
```


# Spatial Density Heatmap 
```{r density_heatmap, echo=FALSE, fig.width=10, fig.height=8}
ggplot(df_analysis_A, aes(x = errorFwd_px_num, y = errorOrth_px)) +
  
  # Reference lines (target at 0,0)
  # Placed BEFORE the heatmap so they sit behind it
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60", linewidth = 0.6) +
  geom_hline(yintercept = 0, linetype = "solid", color = "grey60", linewidth = 0.4) +
  
  # 2D kernel density (heatmap)
  stat_density_2d(
    aes(fill = after_stat(ndensity)),
    geom       = "raster",
    contour    = FALSE,
    n          = 200
  ) +
  
  # Contour lines (thinner and clearer)
  stat_density_2d(
    color      = "white",
    size       = 0.2,
    alpha      = 0.6,
    bins       = 8
  ) +
  
  facet_grid(pathGeometry ~ pathVisible) +
  
  scale_fill_distiller(
    palette = "Spectral",
    direction = -1,
    name = "Relative density"
  ) +

  # Check /visually) if border now perfectly frames the blue heatmap area.
  coord_cartesian(xlim = c(-50, 50), ylim = c(-30, 30), expand = FALSE) +
  
  labs(
    x        = "Forward Error (px)",
    y        = "Orthogonal Error (px)"
  ) +
  
  # APA 7 STYLING 
  theme_classic(base_size = 14) + 
  theme(
    # Strip (Label) Styling - No grey boxes
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold", size = 12, color = "black", margin = margin(b = 8)),
    
    # Axis Styling
    axis.text        = element_text(color = "black", size = 11),
    axis.title       = element_text(face = "bold", size = 13),
    axis.line        = element_blank(), # We use the panel border instead
    
    # Border: Thinner
    panel.border     = element_rect(color = "black", fill = NA, size = 0.5),
    
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    
    legend.position  = "right",
    panel.spacing    = unit(1, "lines") 
  )
```

# Motor Noise (here, Orthogonal Error) Check 

```{r orth_error_precision, echo=FALSE, fig.width=10, fig.height=6}
# JS uses 96 DPI standard (Lines 312-315 of E1_Set1_Horizontal.html)
PX_PER_CM_THEORETICAL <- 96 / 2.54  # ~37.795
THRESHOLD_CM <- 0.5
THRESHOLD_PX <- THRESHOLD_CM * PX_PER_CM_THEORETICAL # ~18.898 px

# Ensure factors for correct coloring
df_analysis_A <- df_analysis_A %>%
  mutate(pathGeometry = factor(pathGeometry, levels = c("linear", "sinusoidal")))

# PART A: MAGNITUDE OF ERROR & BOUNDARY STATISTICS
# This answers: "range of magnitude of error", max/min, and precision.

stats_check <- df_analysis_A %>%
  group_by(pathGeometry) %>%
  summarise(
    Mean_Error_px   = mean(errorOrth_px, na.rm = TRUE),
    
    # "Magnitude of Error" / Precision
    SD_Precision_px = sd(errorOrth_px, na.rm = TRUE), 
    Min_Error_px    = min(errorOrth_px, na.rm = TRUE),
    Max_Error_px    = max(errorOrth_px, na.rm = TRUE),
    
    # Boundary integrity
    Max_Abs_Deviation = max(abs(errorOrth_px), na.rm = TRUE),
    Within_Limit      = max(abs(errorOrth_px), na.rm = TRUE) <= (THRESHOLD_PX + 0.05),
    
    .groups = "drop"
  )

cat("--- INTEGRITY & MAGNITUDE CHECK ---\n")
cat(sprintf("Theoretical Limit (0.5cm): %.2f px\n", THRESHOLD_PX))
print(stats_check)

# PART B: VISUALIZATION (Linear vs. Sinusoidal)
# "I would see a difference between linear and sinusoidal... ranging -20 to +20"

p_dist <- ggplot(df_analysis_A, aes(x = errorOrth_px, fill = pathGeometry)) +
  # Density plot with transparency
  geom_density(alpha = 0.5, color = "grey40") +
  
  # The "Hard Cut" Threshold Lines (The 0.5cm wall at ~18.9px)
  geom_vline(xintercept = c(-THRESHOLD_PX, THRESHOLD_PX), 
             color = "red", linetype = "dashed", size = 1) +
  
  # Center Line (Zero)
  geom_vline(xintercept = 0, color = "black", linetype = "solid", alpha = 0.3) +
  
  # Manual Colors: Linear = Pink, Sinusoidal = Blue
  scale_fill_manual(values = c("linear" = "#FFB6C1", "sinusoidal" = "#87CEEB")) +
  
  # Set the view to just outside the limits so you see the cut-off clearly
  coord_cartesian(xlim = c(-25, 25)) +
  
  labs(
    title = "Orthogonal Error Distribution (Motor Noise)",
    subtitle = paste0("Red dashed lines show the ", round(THRESHOLD_PX, 1), 
                      "px hard cut (0.5cm).\nThis confirms the filter worked."),
    x = "Orthogonal Error (px)",
    y = "Density",
    fill = "Path Geometry"
  ) +
  theme_bw() +
  theme(
    legend.position = "top",
    plot.title = element_text(face="bold"),
    axis.text = element_text(size=11)
  )

print(p_dist)
```


# Main Result Figure (Means + SEM)
## Aggregated at the participant level (N=23) for reliability.

```{r main_result, echo=TRUE}
# Aggregate to Participant Means FIRST
# Uses global df_analysis_A (already normalized)
means_2x2 <- df_analysis_A %>%
  group_by(participant_id, pathGeometry, pathVisible) %>%
  summarize(mean_error = mean(errorFwd_px_num, na.rm = TRUE), .groups = 'drop')

# Calculate Grand Means & SE
summary_stats <- means_2x2 %>%
  group_by(pathGeometry, pathVisible) %>%
  summarise(
    grand_mean = mean(mean_error),
    se = sd(mean_error) / sqrt(n()), 
    .groups = "drop"
  )

# Plot
ggplot(means_2x2, aes(x = pathGeometry, y = mean_error, fill = pathVisible)) +
  geom_point(aes(group = pathVisible), position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.8),
             size = 1.5, alpha = 0.4, color = "grey40", shape = 16, show.legend = FALSE) +
  geom_boxplot(position = position_dodge(width = 0.8), width = 0.5, outlier.shape = NA, 
               alpha = 0.4, color = "black", linewidth = 0.4) +
  geom_errorbar(data = summary_stats, aes(y = grand_mean, ymin = grand_mean - se, ymax = grand_mean + se, group = pathVisible),
                position = position_dodge(width = 0.8), width = 0.2, linewidth = 0.8, color = "black", show.legend = FALSE) +
  geom_point(data = summary_stats, aes(y = grand_mean, shape = pathVisible, group = pathVisible),
             position = position_dodge(width = 0.8), size = 4, color = "black", fill = "black") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  scale_fill_manual(name = "Visibility", values = c("invisible" = "white", "visible" = "grey50")) +
  scale_shape_manual(name = "Visibility", values = c("invisible" = 16, "visible" = 17)) +
  guides(fill = guide_legend(override.aes = list(alpha = 1, color = "black"), keywidth = unit(0.9, "cm"), keyheight = unit(0.9, "cm"))) +
  labs(x = "Path Geometry", y = "Forward Error (px)") +
  theme_classic(base_size = 14) +
  theme(legend.position = "right", legend.title = element_text(face = "bold"), legend.spacing.y = unit(0.5, 'cm'))
```

# Statistical Test: Primary Analysis: RM ANOVA 
## Analysis A: Full Sample (Clean Trials)

```{r rm_anova_primary, echo=TRUE}
rm_anova_clean <- means_2x2 %>%
  mutate(participant_id = factor(participant_id))

# Safety Checks
if(any(is.na(rm_anova_clean$pathGeometry)) || any(is.na(rm_anova_clean$pathVisible))) {
  stop("CRITICAL ERROR: Unexpected factor levels found (generated NAs).")
}

dup_check <- rm_anova_clean %>% count(participant_id, pathGeometry, pathVisible) %>% filter(n != 1)
if(nrow(dup_check) > 0) stop("CRITICAL ERROR: Duplicate cells found! Aggregation failed.")

# Completeness Check
completeness_check <- rm_anova_clean %>%
  distinct(participant_id, pathGeometry, pathVisible) %>%
  count(participant_id, .drop = FALSE) %>%
  mutate(is_complete = n == 4)

valid_ids <- completeness_check %>% filter(is_complete) %>% pull(participant_id)
dropped_ids <- completeness_check %>% filter(!is_complete) %>% pull(participant_id)

rm_anova_final <- rm_anova_clean %>% filter(participant_id %in% valid_ids)

# Check Assumptions (Normality of Residuals)
lm_anova <- lm(mean_error ~ pathGeometry * pathVisible, data = rm_anova_final)
res_anova <- resid(lm_anova)
cat("\n--- Assumption Check: Normality of Residuals (Shapiro-Wilk) ---\n")
print(shapiro.test(res_anova))

# ADDED: Visual Normality Checks for ANOVA
cat("\n--- Visual Assumption Check (ANOVA Residuals) ---\n")
par(mfrow=c(1,2)) 
qqnorm(res_anova); qqline(res_anova)
hist(res_anova, main="ANOVA Residuals", xlab="Residual")
par(mfrow=c(1,1))

stopifnot(all(table(rm_anova_final$participant_id) == 4))
cat("Final Sample for ANOVA:", length(valid_ids), "\n")

if(length(dropped_ids) > 0) {
  cat("Dropped IDs (missing cells):\n")
  print(dropped_ids)
}

# RUN RM-ANOVA (afex)
model_anova <- aov_ez(
  id = "participant_id",
  dv = "mean_error",
  data = rm_anova_final,
  within = c("pathGeometry", "pathVisible"),
  anova_table = list(es = "ges", correction = "none")
)

cat("\n--- PRIMARY ANOVA RESULTS (Type III) ---\n")
print(model_anova)


cat("\n--- CELL MEANS (for Reporting) ---\n")
emm_cells <- emmeans(model_anova, ~ pathGeometry * pathVisible)
print(summary(emm_cells, infer = TRUE, level = 0.95))

cat("\n--- SIMPLE EFFECTS (Visibility within Geometry) ---\n")
emm_interaction <- emmeans(model_anova, ~ pathVisible | pathGeometry)
simple_effects <- contrast(emm_interaction, 
                           method = list("invisible − visible" = c(1, -1)),
                           adjust = "holm")
print(summary(simple_effects, infer = TRUE, level = 0.95))
```

# Extra primary analysis check: trial-level LMM

```{r trial_level_lme, echo=TRUE}
# CONTRAST CODING
# Ensure factors are set
df_analysis_A$pathGeometryC <- ifelse(df_analysis_A$pathGeometry == "sinusoidal", 0.5, -0.5)
df_analysis_A$pathVisibleC  <- ifelse(df_analysis_A$pathVisible  == "visible",    0.5, -0.5)

# SAFETY CHECK
print("--- CODING CHECK: Geometry ---")
print(xtabs(~pathGeometry + pathGeometryC, data = df_analysis_A))
print("--- CODING CHECK: Visibility ---")
print(xtabs(~pathVisible + pathVisibleC, data = df_analysis_A))

# MAXIMAL MODEL
# Formula: Error ~ Interaction + (1 + Interaction | Participant)
#Optimizer: bobyqa

print("Running Maximal LME")

model_A_trial <- lmer(
  errorFwd_px_num ~ pathGeometryC * pathVisibleC +
    (1 + pathGeometryC * pathVisibleC | participant_id),
  data = df_analysis_A,
  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

# CONVERGENCE TROUBLESHOOTING
# If the model above gives "Singular Fit" or fails to converge, run below

#print("--- Running LME (Uncorrelated Random Slopes) ---")

# FALLBACK 1: Remove Correlations (Double Bar ||)
#model_A_trial <- lmer(
 # errorFwd_px_num ~ pathGeometryC * pathVisibleC +
#    (1 + pathGeometryC * pathVisibleC || participant_id),
#  data = df_analysis_A,
 # control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
#)
 
 cat("\n--- SINGULARITY CHECK ---\n")
print(isSingular(model_A_trial, tol = 1e-4))

cat("\n--- CONVERGENCE MESSAGES ---\n")
print(model_A_trial@optinfo$conv$lme4$messages)

# 4. REPORTING (Betas & Significance)
print("--- MODEL SUMMARY (Betas) ---")
print(summary(model_A_trial))

print("--- ANOVA TABLE (Kenward-Roger df) ---")
print(anova(model_A_trial, ddf = "Kenward-Roger")) 

print("--- Simple Effects (Pairwise) ---")
# Specifying 'at' list because predictors are numeric
emm_A <- emmeans(model_A_trial, ~ pathVisibleC | pathGeometryC,
                 at = list(pathGeometryC = c(-0.5, 0.5), pathVisibleC = c(-0.5, 0.5)))


print("--- Tests against Zero (Intercepts) ---")
tests_against_zero <- test(emm_A, null = 0)
print(kable(as.data.frame(tests_against_zero), digits = 3, caption = "T-tests against Target (0)"))

# Visual Confirmation (Plot with Reference Line)
# This plots the estimated means with their confidence intervals relative to 0
plot(emm_A, comparisons = TRUE) + 
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  labs(
    title = "Estimated Marginal Means vs. Veridical Target", 
    subtitle = "Red dashed line = 0 px (Perfect Accuracy). Bars = 95% CIs.",
    x = "Forward Error (px)",
    y = "Condition"
  ) + 
  theme_bw()

cat("\n--- DHARMa Residual Diagnostics (Robustness LME) ---\n")
set.seed(123)
dharma_A <- simulateResiduals(model_A_trial, n = 1000)
plot(dharma_A)
print(testUniformity(dharma_A))
print(testDispersion(dharma_A))
print(testOutliers(dharma_A))
```

# SENSITIVITY CHECK: DATASET B (Global Outliers Removed)
# Rationale: Ensure findings hold when global outliers are excluded.

```{r sensitivity_check_B, echo=TRUE}
if(length(flagged_global) > 0) {
  
  cat("--- SENSITIVITY CHECK: Excluded", length(flagged_global), "Global Outliers ---\n")
  
  # ANOVA SENSITIVITY
  rm_anova_data_B <- df_analysis_B %>%
    group_by(participant_id, pathGeometry, pathVisible) %>%
    summarise(mean_error = mean(errorFwd_px_num, na.rm = TRUE), .groups = "drop") %>%
    mutate(participant_id = factor(participant_id))

  if(any(is.na(rm_anova_data_B$pathGeometry)) || any(is.na(rm_anova_data_B$pathVisible))) {
    stop("CRITICAL ERROR (Dataset B): Unexpected factor levels generated NAs.")
  }
  
  dup_B <- rm_anova_data_B %>% count(participant_id, pathGeometry, pathVisible) %>% filter(n != 1)
  if(nrow(dup_B) > 0) stop("CRITICAL ERROR (Dataset B): Duplicate cells found.")
  
  comp_B <- rm_anova_data_B %>%
    distinct(participant_id, pathGeometry, pathVisible) %>%
    count(participant_id, .drop = FALSE) %>%
    mutate(is_complete = n == 4)
  
  valid_ids_B <- comp_B %>% filter(is_complete) %>% pull(participant_id)
  rm_anova_B_final <- rm_anova_data_B %>% filter(participant_id %in% valid_ids_B)
  
  model_anova_B <- aov_ez(
    id = "participant_id", dv = "mean_error", data = rm_anova_B_final,
    within = c("pathGeometry", "pathVisible"),
    anova_table = list(es = "ges", correction = "none")
  )
  print("--- Sensitivity: RM-ANOVA Results (Dataset B) ---")
  print(model_anova_B)
  
  # LME ROBUSTNESS SENSITIVITY
  df_analysis_B$pathGeometryC <- ifelse(df_analysis_B$pathGeometry == "sinusoidal", 0.5, -0.5)
  df_analysis_B$pathVisibleC  <- ifelse(df_analysis_B$pathVisible  == "visible",    0.5, -0.5)
  
  model_B_trial <- lmer(
    errorFwd_px_num ~ pathGeometryC * pathVisibleC +
      (1 + pathGeometryC * pathVisibleC || participant_id),
    data = df_analysis_B,
    control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
  )
  
  print("--- Sensitivity: Trial-Level LME Results (Dataset B) ---")
  print(anova(model_B_trial, ddf = "Kenward-Roger"))

  # ADDED: Visual Normality Check
  cat("\n--- Visual Normality Check (LME B Residuals) ---\n")
  qqnorm(resid(model_B_trial), main="QQ Plot: LME B Residuals"); qqline(resid(model_B_trial))

  cat("\n--- DHARMa Residual Diagnostics (Dataset B) ---\n")
  set.seed(123)
  dharma_B <- simulateResiduals(model_B_trial, n = 1000)
  plot(dharma_B)
  print(testUniformity(dharma_B))
  print(testDispersion(dharma_B))
  print(testOutliers(dharma_B))
  
} else {
  print("No global outliers detected. Dataset B is identical to Dataset A.")
}
```


# SECOND-LEVEL ANALYSIS: STEP 1: Group Splits based on Linear Baseline

```{r step1info, echo=TRUE}
linear_baseline <- df_analysis_A %>%
  filter(pathGeometry == "linear", pathVisible == "invisible") %>%
  group_by(participant_id) %>%
  summarise(
    # Using the signed mean here to know if they went Forward or Backward
    linear_mean_signed = mean(errorFwd_px_num, na.rm = TRUE),
    .groups = "drop"
  )

median_val <- median(linear_baseline$linear_mean_signed)

ppt_groups <- linear_baseline %>%
  mutate(
    # --- METHOD A: "ABSOLUTE SPLIT" (Criterion = 0) ---
    # Defining groups based on absolute direction relative to the target (0).
    Group_Absolute = case_when(
      linear_mean_signed >= 0 ~ "Momentum (+)",
      linear_mean_signed < 0  ~ "Repulsion (-)"
    ),
    
    # --- METHOD B: "MEDIAN SPLIT" (Criterion = Median) ---
    # Defining groups based on relative position to the group average.
    Group_Median = case_when(
      linear_mean_signed >= median_val ~ "High Shift (>Med)",
      linear_mean_signed < median_val  ~ "Low Shift (<Med)"
    )
  )

# Check N per group
print("--- Method A: Absolute Split (Zero Cutoff) ---")
print(table(ppt_groups$Group_Absolute))

print(paste0("--- Method B: Median Split (Median = ", round(median_val, 2), "px) ---"))
print(table(ppt_groups$Group_Median))

# Analyzing how these groups performed on the Sinusoidal trials
df_grouped <- df_analysis_A %>%
  left_join(ppt_groups %>% select(participant_id, Group_Absolute, Group_Median), by = "participant_id") %>%
  filter(pathGeometry == "sinusoidal")

# VISUALIZATION (Comparison)

p_abs <- ggplot(df_grouped, aes(x = Group_Absolute, y = errorFwd_px_num, fill = Group_Absolute)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3, fill = "white") +
  scale_fill_manual(values = c("Momentum (+)" = "white", "Repulsion (-)" = "white")) +
  labs(
    title = "Method A: Absolute Split",
    subtitle = "Groups defined by Positive/Negative Linear Bias",
    y = "Sinusoidal Error (px)", x = NULL
  ) +
  theme_bw() + theme(legend.position = "none")

p_med <- ggplot(df_grouped, aes(x = Group_Median, y = errorFwd_px_num, fill = Group_Median)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3, fill = "white") +
  scale_fill_manual(values = c("High Shift (>Med)" = "white", "Low Shift (<Med)" = "white")) +
  labs(
    title = "Method B: Median Split",
    subtitle = "Groups defined by Linear Median Split",
    y = NULL, x = NULL
  ) +
  theme_bw() + theme(legend.position = "none")

gridExtra::grid.arrange(p_abs, p_med, ncol = 2)


# T-TESTS (Participant Level)
# Summarize sinusoidal data to participant level
sinu_summary <- df_grouped %>%
  group_by(participant_id, Group_Absolute, Group_Median) %>%
  summarise(sinu_mean = mean(errorFwd_px_num, na.rm = TRUE), .groups = "drop")

print("--- T-Test: Absolute Split ---")
print(t.test(sinu_mean ~ Group_Absolute, data = sinu_summary))

print("--- T-Test: Median Split ---")
print(t.test(sinu_mean ~ Group_Median, data = sinu_summary))


# TESTS AGAINST ZERO 
# Goal: Test if each group is significantly different from 0 (One-sample t-test)
# Correction: Bonferroni for 6 tests (3 Expts x 2 Groups) -> 0.05 / 6 = 0.0083

# High Shift Group (> Median)
# Subset: Take 'sinu_summary', filter for High Shift, pull the 'sinu_mean' column
data_high <- subset(sinu_summary, Group_Median == "High Shift (>Med)")$sinu_mean
t_high <- t.test(data_high, mu = 0)

print("--- Test Against 0: High Shift Group ---")
print(t_high)

# Low Shift Group (< Median)
# Subset: Take 'sinu_summary', filter for Low Shift, pull the 'sinu_mean' column
data_low <- subset(sinu_summary, Group_Median == "Low Shift (<Med)")$sinu_mean
t_low <- t.test(data_low, mu = 0)

print("--- Test Against 0: Low Shift Group ---")
print(t_low)

# Significance Check
alpha_bonferroni <- 0.05 / 6

cat("\n--- Bonferroni Correction Check (Alpha =", round(alpha_bonferroni, 5), ") ---\n")
cat("Is High Shift significantly > 0?  ", t_high$p.value < alpha_bonferroni, "\n")
cat("Is Low Shift significantly < 0?   ", t_low$p.value < alpha_bonferroni, "\n")
```

# STEP 2: REPEAT MAIN ANALYSES BY GROUP  (USING MEDIAN SPLIT)
## "Do path manipulations have different effects for these two participant types?"

```{r repat, echo=TRUE}
# 1. PREPARE DATA & CONTRASTS
df_grouped_full <- df_analysis_A %>%
  left_join(ppt_groups %>% select(participant_id, Group_Median), by = "participant_id") %>%
  filter(!is.na(Group_Median))

# Manual Contrast Coding for Group
df_grouped_full$GroupC <- ifelse(df_grouped_full$Group_Median == "Low Shift (<Med)", 0.5, -0.5)

# 2. VISUALIZATION: Main Results split by Group
means_grouped <- df_grouped_full %>%
  group_by(participant_id, Group_Median, pathGeometry, pathVisible) %>%
  summarise(mean_error = mean(errorFwd_px_num, na.rm = TRUE), .groups = 'drop')

ggplot(means_grouped, aes(x = pathGeometry, y = mean_error, fill = pathVisible)) +
  
  # 1. Reference Line
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  
  # 2. Boxplots (Transparent & Elegant)
  geom_boxplot(
    position = position_dodge(width = 0.8),
    width = 0.5,
    outlier.shape = NA,
    alpha = 0.4,
    color = "black",
    lwd = 0.4
  ) +
  
  # 3. Individual Jittered Points
  geom_point(
    position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.8),
    size = 1.5, 
    alpha = 0.4, 
    color = "grey40",
    show.legend = FALSE # Keep legend clean
  ) +
  
  # 4. Faceting (Split by Group)
  facet_wrap(~Group_Median) +
  
  # 5. APA Colors (High Contrast)
  scale_fill_manual(name = "Visibility", values = c("invisible" = "white", "visible" = "grey50")) +
  
  # 6. Make Legend Readable (Opaque & Large)
  guides(
    fill = guide_legend(
      override.aes = list(alpha = 1, color = "black"),
      keywidth = unit(0.9, "cm"),
      keyheight = unit(0.9, "cm")
    )
  ) +
  
  labs(
    y = "Mean Forward Error (px)",
    x = "Path Geometry"
  ) +
  
  # 7. APA 7 THEME + SPACING + GRIDS
  theme_classic(base_size = 14) +
  theme(
    # --- TIGHTER SPACING ---
    aspect.ratio = 2.0,
    
    # --- FAINT GRID LINES RESTORED ---
    # Horizontal only (light grey) to help read the Y-axis values
    panel.grid.major.y = element_line(color = "grey92", size = 0.3),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    
    # Clean Headers (No Grey Boxes)
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    
    # Elegant Borders
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    axis.line = element_blank(), 
    
    # --- LEGEND CENTERED ---
    legend.position = "right",
    legend.justification = "center",
    legend.title = element_text(face = "bold")
  )

# 3. STATISTICAL MODEL
model_group_interaction <- lmer(
  errorFwd_px_num ~ pathGeometryC * pathVisibleC * GroupC + 
  (1 + pathGeometryC * pathVisibleC || participant_id), 
  data = df_grouped_full,
  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

# 4. REPORTING
print("--- Model Summary (Betas) ---")
print(summary(model_group_interaction))

print("--- ANOVA Table (Kenward-Roger) ---")
print(anova(model_group_interaction, ddf = "Kenward-Roger"))

# 5. FOLLOW-UP CONTRASTS
my_levels <- list(
  pathGeometryC = c(-0.5, 0.5), 
  pathVisibleC  = c(-0.5, 0.5),
  GroupC        = c(-0.5, 0.5)
)

print("--- Simple Effects: Geometry Effect split by Group ---")
emm_interaction <- emmeans(model_group_interaction, ~ pathGeometryC | GroupC, at = my_levels)
print(pairs(emm_interaction))
```
```

# Secondary Analysis Extra Sanity Check: Mixed ANOVA

```{r sanity_check_anova_secondary, echo=TRUE}

# Rationale: Confirm that the Group x Geometry x Visibility interaction holds up under standard OLS assumptions (to rule out LME artifacts).

# Factors: Group (Between), Geometry (Within), Visibility (Within)
mixed_anova_data <- df_grouped_full %>%
  group_by(participant_id, Group_Median, pathGeometry, pathVisible) %>%
  summarise(mean_error = mean(errorFwd_px_num, na.rm = TRUE), .groups = "drop")

# need complete 2x2 data for every participant
completeness_check_group <- mixed_anova_data %>%
  count(participant_id) %>%
  mutate(is_complete = n == 4)

valid_ids_group <- completeness_check_group %>% filter(is_complete) %>% pull(participant_id)
dropped_ids_group <- completeness_check_group %>% filter(!is_complete) %>% pull(participant_id)

mixed_anova_clean <- mixed_anova_data %>%
  filter(participant_id %in% valid_ids_group)

cat("--- Mixed ANOVA Data Integrity ---\n")
if(length(dropped_ids_group) > 0) {
  cat("WARNING: IDs dropped due to missing cells:", length(dropped_ids_group), "\n")
} else {
  cat("Status: Balanced Dataset for Mixed ANOVA.\n")
}

# Formula: Error ~ Between * Within + Error(Subject/Within)
cat("\n--- Running Standard Mixed ANOVA (Group x Geo x Vis) ---\n")

mixed_model <- aov(
  mean_error ~ Group_Median * pathGeometry * pathVisible + 
  Error(participant_id / (pathGeometry * pathVisible)), 
  data = mixed_anova_clean
)


print(summary(mixed_model))

cat("\n--- COMPARISON GUIDE ---\n")
cat("Look for the 3-way interaction: Group_Median:pathGeometry:pathVisible\n")
cat("Does the p-value match the LME conclusion?\n")
```

# SECONDARY ANALYSIS: MIXED ANCOVA (SPLIT-HALF VALIDATED)
# To examine if individual differences in baseline shift moderate 
# the effects of Geometry and Visibility.
# Method: Split-Half Independence to prevent circularity.
#   - COVARIATE (Baseline Shift) is calculated from ODD trials of Linear-Invisible.
#   - DV (Mean Error) is calculated from the REMAINING trials (Even Linear-Inv + All others).

```{r secondary_ancova_splithalf, echo=TRUE}
# ETUP: MARK ODD/EVEN TRIALS 
df_split_prep <- df_analysis_A %>%
  mutate(is_odd_trial = (trial %% 2) != 0)

# CALCULATE INDEPENDENT COVARIATE (Predictor)
# ONLY the ODD trials of the Linear-Invisible condition
baseline_shift_indep <- df_split_prep %>%
  filter(pathGeometry == "linear", pathVisible == "invisible", is_odd_trial == TRUE) %>%
  group_by(participant_id) %>%
  summarise(
    shift_linear_invis_odd = mean(errorFwd_px_num, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    # Z-score for interprettability in the interaction model
    shift_z = as.numeric(scale(shift_linear_invis_odd))
  )

cat("\n--- Independent Covariate Summary (ODD Trials Only) ---\n")
print(summary(baseline_shift_indep$shift_linear_invis_odd))

# REMOVE the specific trials used for the covariate to break circularity.
# keep: Even Linear-Invisible trials AND All trials from other conditions.
df_ancova_trials <- df_split_prep %>%
  filter(!(pathGeometry == "linear" & pathVisible == "invisible" & is_odd_trial == TRUE))

# Aggregate to Cell Means (1 row per participant per condition)
df_ancova_valid <- df_ancova_trials %>%
  group_by(participant_id, pathGeometry, pathVisible) %>%
  summarise(mean_error = mean(errorFwd_px_num, na.rm = TRUE), .groups = "drop") %>%
  # Join the independent covariate
  left_join(baseline_shift_indep, by = "participant_id")

# Contrast Coding (Crucial for Type III SS)
df_ancova_valid$pathGeometryC <- ifelse(df_ancova_valid$pathGeometry == "sinusoidal", 0.5, -0.5)
df_ancova_valid$pathVisibleC  <- ifelse(df_ancova_valid$pathVisible  == "visible",    0.5, -0.5)

# RUN MIXED ANCOVA (LME on Cell Means) 
# Formula: Error ~ Geometry * Visibility * Baseline_Shift + (1 | Participant)
# Note: With cell means, only fit random intercepts.
model_ancova_valid <- lmer(
  mean_error ~ pathGeometryC * pathVisibleC * shift_z + (1 | participant_id),
  data = df_ancova_valid,
  control = lmerControl(optimizer = "bobyqa")
)

cat("\n--- Secondary Analysis: Mixed ANCOVA Results (Split-Half Validated) ---\n")
# ANOVA table with Kenward-Roger correction
print(anova(model_ancova_valid, ddf = "Kenward-Roger"))

cat("\n--- Model Summary (Betas) ---\n")
print(summary(model_ancova_valid))

# SIMPLE SLOPES PROBE (Decomposing the Interaction) 
# heck the Geometry x Visibility interaction at Low (-1SD), Mean, and High (+1SD) Shift
emm_ancova_valid <- emmeans(
  model_ancova_valid, ~ pathVisibleC * pathGeometryC | shift_z,
  at = list(pathGeometryC = c(-0.5, 0.5), pathVisibleC = c(-0.5, 0.5), shift_z = c(-1, 0, 1))
)

cat("\n--- Interaction Pattern at -1SD, Mean, +1SD Baseline Shift ---\n")
print(contrast(emm_ancova_valid, interaction = "pairwise", adjust="holm"))

# DIAGNOSTICS (DHARMa) 
cat("\n--- DHARMa Residual Diagnostics (Split-Half Model) ---\n")
set.seed(123)
dharma_ancova_v <- simulateResiduals(model_ancova_valid, n = 1000)
plot(dharma_ancova_v)
print(testUniformity(dharma_ancova_v))
print(testOutliers(dharma_ancova_v))

# VISUALIZATION (Descriptive Plot)
# Note: The statistical test above is continuous. This plot uses a median split
# purely for visual clarity to show the reader the pattern.
median_shift <- median(baseline_shift_indep$shift_linear_invis_odd, na.rm = TRUE)

plot_groups_valid <- baseline_shift_indep %>%
  mutate(
    shift_plot_group = ifelse(
      shift_linear_invis_odd >= median_shift, "High Shift (>Med)", "Low Shift (<Med)"
    )
  )

plot_data_valid <- df_ancova_valid %>%
  left_join(plot_groups_valid %>% select(participant_id, shift_plot_group), by = "participant_id") %>%
  filter(!is.na(shift_plot_group))

ggplot(plot_data_valid, aes(x = pathGeometry, y = mean_error, fill = pathVisible)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey60") +
  geom_boxplot(position = position_dodge(width = 0.8), width = 0.55, outlier.shape = NA, alpha = 0.45) +
  geom_point(position = position_jitterdodge(jitter.width = 0.10, dodge.width = 0.8), size = 1.5, alpha = 0.45) +
  facet_wrap(~shift_plot_group) +
  scale_fill_manual(values = c("invisible" = "white", "visible" = "grey70"), name = "Visibility") +
  labs(
    title = "Moderation by Baseline Shift (Split-Half)",
    subtitle = "Covariate calc. from ODD trials; Data from EVEN/Remaining trials.",
    x = "Path Geometry",
    y = "Mean Forward Error (px)"
  ) +
  theme_classic(base_size = 14) +
  theme(strip.background = element_blank(), strip.text = element_text(face = "bold"))

# VISUALIZATION (Continuous Interaction) 
# Rationale: Visualize the moderation effect directly without arbitrary binning.
# X-axis: Baseline Shift (from ODD trials)
# Y-axis: Mean Error (from REMAINING trials)
# Facets: Path Geometry
# Lines: Regression slopes for Visibility

ggplot(df_ancova_valid, aes(x = shift_linear_invis_odd, y = mean_error, color = pathVisible, fill = pathVisible)) +
  
  # 1. Reference lines (Zero error / Zero shift)
  geom_hline(yintercept = 0, linetype = "solid", color = "grey80") +
  geom_vline(xintercept = 0, linetype = "solid", color = "grey80") +

  # 2. Individual Participant Points (Jittered slightly to avoid overlap)
  geom_point(alpha = 0.6, size = 2) +

  # 3. Linear Regression Lines with Confidence Intervals
  geom_smooth(method = "lm", alpha = 0.2, fullrange = TRUE) +

  # 4. Facet by Geometry to see the effect in Linear vs Sinusoidal
  facet_wrap(~pathGeometry) +

  # 5. Styling (High Contrast for Lines)
  scale_color_manual(values = c("invisible" = "black", "visible" = "#E69F00"), name = "Visibility") +
  scale_fill_manual(values = c("invisible" = "grey20", "visible" = "#E69F00"), name = "Visibility") +

  labs(
    title = "Continuous Moderation by Baseline Shift (Split-Half)",
    subtitle = "Regression lines show how the Visibility effect changes as Baseline Shift increases.",
    x = "Baseline Shift (px) [from Independent ODD trials]",
    y = "Mean Forward Error (px) [from Test trials]"
  ) +
  
  theme_classic(base_size = 14) +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    legend.position = "bottom",
    # Add spacing to title
    plot.subtitle = element_text(margin = margin(b = 10), size = 11, face = "italic")
  )
```


#  SAVE FINAL DATA FOR CROSS-EXPERIMENT COMPARISON 
```{r save, echo=TRUE}
if(!exists("baseline_shift")) {
  baseline_shift <- df_analysis_A %>%
    filter(pathGeometry == "linear", pathVisible == "invisible") %>%
    group_by(participant_id) %>%
    summarise(shift_linear_invis = mean(errorFwd_px_num, na.rm = TRUE), .groups = "drop") %>%
    mutate(shift_z = as.numeric(scale(shift_linear_invis)))
}

df_for_mega <- df_analysis_A %>%
  left_join(baseline_shift %>% select(participant_id, shift_linear_invis, shift_z), by = "participant_id") %>%
  mutate(experiment = "E1_horizontal")

# Generic
output_path <- "/Users/E1_Processed_Data.csv"
write_csv(df_for_mega, output_path)

cat("E1 Processed Data Saved (includes continuous 'shift_z').\n")
```


```{r session_info, echo=FALSE}
sessionInfo()
```
