---
title: "Cross-Experiment Comparison: The Grand Finale"
author: "Analysis Pipeline"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(eval = FALSE, echo = TRUE, fig.width = 12, fig.height = 8, message = FALSE, warning = FALSE)

library(tidyverse)
library(lmerTest)
library(emmeans)
library(knitr)
```

# Prep 

```{r dataload}
# 1. Load the data  saved from the previous steps
#    (These ave the "Group_Median" column!)

# Paths are generic.
path_E1 <- "data/processed/E1_Processed_Data.csv"
path_E2 <- "data/processed/E2_Processed_Data.csv"
path_E3 <- "data/processed/E3_Processed_Data.csv"

# 2. Load & Create Unique IDs
cols_to_keep <- c("participant_id", "trial", "pathGeometry", "pathVisible", 
                  "errorFwd_px_num", "Group_Median")

df_E1 <- read_csv(path_E1_processed, show_col_types = FALSE) %>% 
  mutate(
    Experiment = "Horizontal (E1)",
    unique_id = paste0("E1_", participant_id) 
  )

df_E2 <- read_csv(path_E2_processed, show_col_types = FALSE) %>% 
  mutate(
    Experiment = "Upward (E2)",
    unique_id = paste0("E2_", participant_id) 
  )

df_E3 <- read_csv(path_E3_processed, show_col_types = FALSE) %>% 
  mutate(
    Experiment = "Downward (E3)",
    unique_id = paste0("E3_", participant_id) 
  )

# Merge into Mega-Dataset (Added df_E2 to bind_rows)
df_mega <- bind_rows(df_E1, df_E2, df_E3) %>%
  mutate(
    Experiment = factor(Experiment, levels = c("Horizontal (E1)", "Upward (E2)", "Downward (E3)")),
    pathGeometry = factor(pathGeometry, levels = c("linear", "sinusoidal")),
    pathVisible = factor(pathVisible, levels = c("invisible", "visible")),
    Group_Median = factor(Group_Median, levels = c("High Shift (>Med)", "Low Shift (<Med)"))
  )

# ONTRAST CODING (Manual Numeric Contrasts)
# Within-Subject Factors (2 levels) -> -0.5 / 0.5
df_mega$pathGeometryC <- ifelse(df_mega$pathGeometry == "sinusoidal", 0.5, -0.5)
df_mega$pathVisibleC  <- ifelse(df_mega$pathVisible  == "visible",    0.5, -0.5)

# Between-Subject Factor (2 levels) -> -0.5 / 0.5
df_mega$GroupC        <- ifelse(df_mega$Group_Median == "Low Shift (<Med)", 0.5, -0.5)

# Experiment Factor (3 levels) -> Sum-to-zero contrasts (Effect coding)
# This ensures ANOVA main effects are tested against the grand mean
contrasts(df_mega$Experiment) <- contr.sum(3)

# SAFETY CHECKS 
print("--- CODING CHECK: Geometry ---")
print(xtabs(~pathGeometry + pathGeometryC, data = df_mega))

print("--- CODING CHECK: Visibility ---")
print(xtabs(~pathVisible + pathVisibleC, data = df_mega))

print("--- CODING CHECK: Group ---")
print(xtabs(~Group_Median + GroupC, data = df_mega))

print("--- CODING CHECK: Experiment (Contrast Matrix) ---")
print(contrasts(df_mega$Experiment))

print("Mega-Dataset Loaded Successfully.")
print(paste("Total Participants:", length(unique(df_mega$unique_id))))
```

##Visualization: The "Grand Finale" Plots

```{r plot, echo=FALSE}
## Visualization: The "Grand Finale" Plots (Methods Figure Style)

#  AGGREGATE TO PARTICIPANT LEVEL
df_participant_means <- df_mega %>%
  group_by(participant_id, Experiment, Group_Median, pathGeometry, pathVisible) %>%
  summarise(mean_error = mean(errorFwd_px_num, na.rm = TRUE), .groups = "drop")

apa_theme <- theme_classic(base_size = 14) +
  theme(
    # Faint Grid Lines (Horizontal only)
    panel.grid.major.y = element_line(color = "grey92", size = 0.3),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    
    # Clean Panel Borders
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    axis.line = element_blank(),
    
    # Legend Styling
    legend.position = "right",
    legend.title = element_text(face = "bold"),
    
    # X-Axis Spacing
    axis.text.x = element_text(color = "black", size = 11)
  )

# PLOT 1: PRIMARY ANALYSIS (Global Trends)
# X-Axis = Experiment (E1, E2, E3)
# Facet  = Geometry (Linear vs. Sinusoidal)
# Fill   = Visibility (Invisible vs. Visible)

ggplot(df_participant_means, aes(x = Experiment, y = mean_error, fill = pathVisible)) +
  
  # Reference Line
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  
  # Boxplots
  geom_boxplot(
    position = position_dodge(width = 0.8),
    width = 0.6,
    outlier.shape = NA,
    alpha = 0.4,
    color = "black",
    lwd = 0.4
  ) +
  
  # Jittered Points
  geom_point(
    aes(group = pathVisible),
    position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.8),
    size = 1.2,
    alpha = 0.4,
    color = "grey40",
    show.legend = FALSE
  ) +
  
  # FACET: Rows = Geometry
  facet_grid(pathGeometry ~ .) +
  
  # Colors
  scale_fill_manual(name = "Visibility", values = c("invisible" = "white", "visible" = "grey80")) +
  guides(fill = guide_legend(override.aes = list(alpha = 1, color = "black"))) +
  
  # Labels
  labs(
    title = "Primary Analysis: Global Trends (The Gravity Arc)",
    y = "Mean Forward Error (px)",
    x = "Motion Axis (Experiment)"
  ) +
  
  apa_theme


# PLOT 2: SECONDARY ANALYSIS (Subgroups)
# X-Axis = Experiment
# Facet  = Geometry (Rows) x Group (Cols)
# Fill   = Visibility

ggplot(df_participant_means, aes(x = Experiment, y = mean_error, fill = pathVisible)) +
  
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  
  geom_boxplot(
    position = position_dodge(width = 0.8),
    width = 0.6,
    outlier.shape = NA,
    alpha = 0.4,
    color = "black",
    lwd = 0.4
  ) +
  
  geom_point(
    aes(group = pathVisible),
    position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.8),
    size = 1.0,
    alpha = 0.4,
    color = "grey40",
    show.legend = FALSE
  ) +
  
  # FACET: Rows = Geometry, Columns = Group
  facet_grid(pathGeometry ~ Group_Median) +
  
  scale_fill_manual(name = "Visibility", values = c("invisible" = "white", "visible" = "grey80")) +
  guides(fill = guide_legend(override.aes = list(alpha = 1, color = "black"))) +
  
  labs(
    title = "Secondary Analysis: Subgroup Strategies",
    subtitle = "Comparing High vs. Low Shifters across Experiments",
    y = "Mean Forward Error (px)",
    x = "Motion Axis (Experiment)"
  ) +
  
  apa_theme +
  theme(legend.position = "bottom")
```

## Primary Inferential Analysis: Mixed ANOVA 

```{r jd, echo=FALSE}

# PRIMARY ANALYSIS: STANDARD MIXED ANOVA

# Goal: Establish general trends (Experiment x Geometry x Visibility)
# Structure: Aggregated Participant Means

rm_anova_data <- df_mega %>%
  group_by(unique_id, Experiment, pathGeometry, pathVisible) %>%
  summarise(mean_error = mean(errorFwd_px_num, na.rm = TRUE), .groups = "drop")

# CHECK DATA INTEGRITY
completeness_check <- rm_anova_data %>%
  count(unique_id) %>%
  mutate(is_complete = n == 4) # Must have 4 repeated measures (2 geo * 2 vis)

valid_ids <- completeness_check %>% filter(is_complete) %>% pull(unique_id)
rm_anova_clean <- rm_anova_data %>% filter(unique_id %in% valid_ids)

cat("--- Primary ANOVA Data Check ---\n")
cat("Participants Included:", length(valid_ids), "\n")

# RUN MODEL
# Between: Experiment
# Within:  pathGeometry, pathVisible
print("--- Running Primary Repeated Measures ANOVA ---")

primary_model <- aov(
  mean_error ~ Experiment * pathGeometry * pathVisible + 
  Error(unique_id / (pathGeometry * pathVisible)), 
  data = rm_anova_clean
)

summary(primary_model)
```

## Secondary Inferential Analysis: LMM (Subgroups)

```{r secondary_lmm, echo=TRUE}

# Goal: Analyze Subgroup Strategies (Group x Exp x Geo x Vis)
# Structure: Trial-Level Data with Random Slopes

print("--- Running Secondary Mega-Model (LMM) ---")

# Ensure proper factoring before running the model
df_mega$Experiment <- factor(df_mega$Experiment, levels = c("Horizontal (E1)", "Upward (E2)", "Downward (E3)"))
contrasts(df_mega$Experiment) <- contr.sum(3) # Effect coding: 1=E1, 2=E2, 3=Hidden(E3)

cat("\n--- SINGULARITY CHECK ---\n")
print(isSingular(model_A_trial, tol = 1e-4))

cat("\n--- CONVERGENCE MESSAGES ---\n")
print(model_A_trial@optinfo$conv$lme4$messages)

# Run the Model
model_mega <- lmer(
  errorFwd_px_num ~ Experiment * pathGeometryC * pathVisibleC * GroupC + 
  (1 + pathGeometryC * pathVisibleC | unique_id),
  data = df_mega,
  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

# 1. FIXED EFFECTS (BETA WEIGHTS)
print("--- Fixed Effects Coefficients (Beta Weights) ---")
# Note: Experiment1 = E1 effect; Experiment2 = E2 effect; E3 is the baseline reference in sum coding.
print(summary(model_mega)$coefficients)

# 2. OMNIBUS F-TESTS (Type III Kenward-Roger)
print("--- Secondary Analysis ANOVA (Kenward-Roger) ---")
print(anova(model_mega, ddf = "Kenward-Roger"))
```

## Follow-up Contrasts (Secondary Analysis)

```{r follow-up-contrasts, echo=FALSE}
# Set up levels for Emmeans (Numeric Coding)
my_levels <- list(
  pathGeometryC = c(-0.5, 0.5), 
  pathVisibleC  = c(-0.5, 0.5),
  GroupC        = c(-0.5, 0.5)
)

# 1. EXPERIMENT TRENDS (The "Gravity Arc")

cat("\n--- 1. Experiment Trends (E1 vs E2 vs E3) within Geometry * Visibility Cells ---\n")
emm_exp_trends <- emmeans(model_mega, ~ Experiment | pathGeometryC * pathVisibleC, at = my_levels)
print(pairs(emm_exp_trends, adjust = "bonferroni"))

# 2. VISIBILITY EFFECTS (The "Damping" Effect)

cat("\n--- 2. Visibility Effects (Invisible - Visible) within Experiment * Geometry ---\n")
emm_vis_effects <- emmeans(model_mega, ~ pathVisibleC | Experiment * pathGeometryC, at = my_levels)
print(pairs(emm_vis_effects, adjust = "bonferroni"))

# 3. SUBGROUP STRATIFICATION

cat("\n--- 3. Subgroup Analysis: Geometry * Visibility Interaction within Groups ---\n")

# A. Interaction Contrasts
emm_group_interaction <- emmeans(model_mega, ~ pathGeometryC * pathVisibleC | GroupC, at = my_levels)
print(contrast(emm_group_interaction, interaction = c("pairwise", "pairwise"), adjust = "bonferroni"))

# B. Simple Effects of Visibility within Geometry * Group
cat("\n--- Simple Effects: Visibility differences within Geometry & Group ---\n")
emm_vis_by_geo_group <- emmeans(model_mega, ~ pathVisibleC | pathGeometryC * GroupC, at = my_levels)
print(pairs(emm_vis_by_geo_group, adjust = "bonferroni"))
```

# SECONDARY ANALYSIS: CROSS-EXPERIMENT CONTINUOUS MODERATION (SPLIT-HALF)
# Rationale: To determine if the Baseline Shift moderation effect found in individual 
# experiments is robust across all motion axes (Horizontal, Upward, Downward).
# Method: 
#   - COVARIATE: Baseline Shift (Linear-Invisible, ODD trials).
#   - DV: Mean Error (REMAINING trials).
#   - MODEL: Adds 'Experiment' to test the 4-way interaction.

```{r cross_ancova_splithalf, echo=TRUE, message=FALSE, warning=FALSE}

df_split_prep <- df_mega %>%
  mutate(is_odd_trial = (trial %% 2) != 0)

# CALCULATE INDEPENDENT COVARIATE (Predictor) 
# Grouping by 'unique_id'; don't mix participants from different experiments!
baseline_shift_indep <- df_split_prep %>%
  filter(pathGeometry == "linear", pathVisible == "invisible", is_odd_trial == TRUE) %>%
  group_by(unique_id, Experiment) %>% # Keep Experiment for plotting/merging later
  summarise(
    shift_linear_invis_odd = mean(errorFwd_px_num, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    # Z-score for interpretability (Grand-mean centered across all experiments)
    shift_z = as.numeric(scale(shift_linear_invis_odd))
  )

cat("\n--- Independent Covariate Summary (ODD Trials Only) ---\n")
print(summary(baseline_shift_indep$shift_linear_invis_odd))

# PREPARE ANALYSIS DATA (Outcome)
# Remove the ODD Linear-Invisible trials used for the covariate.
df_ancova_trials <- df_split_prep %>%
  filter(!(pathGeometry == "linear" & pathVisible == "invisible" & is_odd_trial == TRUE))

# Aggregate to Cell Means (1 row per participant per condition)
df_ancova_valid <- df_ancova_trials %>%
  group_by(unique_id, Experiment, pathGeometry, pathVisible) %>%
  summarise(mean_error = mean(errorFwd_px_num, na.rm = TRUE), .groups = "drop") %>%
  # Join the independent covariate
  left_join(baseline_shift_indep, by = c("unique_id", "Experiment"))

# Contrast Coding
# Geometry & Visibility: Effect coding (-0.5, 0.5)
df_ancova_valid$pathGeometryC <- ifelse(df_ancova_valid$pathGeometry == "sinusoidal", 0.5, -0.5)
df_ancova_valid$pathVisibleC  <- ifelse(df_ancova_valid$pathVisible  == "visible",    0.5, -0.5)

# Experiment: Sum-to-zero contrasts (matching primary analysis)
df_ancova_valid$Experiment <- factor(df_ancova_valid$Experiment, 
                                     levels = c("Horizontal (E1)", "Upward (E2)", "Downward (E3)"))
contrasts(df_ancova_valid$Experiment) <- contr.sum(3)

# ´RUN MEGA-MODEL (Mixed ANCOVA) 
# Formula: Error ~ Experiment * Geometry * Visibility * Baseline_Shift + (1 | Participant)
# look for the 4-way interaction (Experiment:Geometry:Visibility:Shift) to see if the moderation pattern differs by Experiment.
model_ancova_mega <- lmer(
  mean_error ~ Experiment * pathGeometryC * pathVisibleC * shift_z + (1 | unique_id),
  data = df_ancova_valid,
  control = lmerControl(optimizer = "bobyqa")
)

cat("\n--- Cross-Experiment ANCOVA Results (Split-Half Validated) ---\n")
# ANOVA table with Kenward-Roger correction
print(anova(model_ancova_mega, ddf = "Kenward-Roger"))

# SIMPLE SLOPES PROBE
# want to see if the Baseline Shift effect holds generally.
# probe the Geometry x Visibility x Shift interaction (averaged over Experiment if 4-way is ns)
emm_ancova_mega <- emmeans(
  model_ancova_mega, ~ pathVisibleC * pathGeometryC | shift_z,
  at = list(pathGeometryC = c(-0.5, 0.5), pathVisibleC = c(-0.5, 0.5), shift_z = c(-1, 0, 1))
)

cat("\n--- Interaction Pattern at -1SD, Mean, +1SD Baseline Shift (Averaged across Exps) ---\n")
print(contrast(emm_ancova_mega, interaction = "pairwise", adjust="holm"))

# VISUALIZATION (Continuous Interaction by Experiment) 
# do slopes look similar across E1, E2, and E3.

ggplot(df_ancova_valid, aes(x = shift_linear_invis_odd, y = mean_error, color = pathVisible, fill = pathVisible)) +
  # Reference lines
  geom_hline(yintercept = 0, linetype = "solid", color = "grey85") +
  
  # Individual Points
  geom_point(alpha = 0.4, size = 1.5) +
  
  # Linear Regression Lines
  geom_smooth(method = "lm", alpha = 0.2, fullrange = FALSE) +
  
  facet_grid(Experiment ~ pathGeometry) +
  
   scale_color_manual(values = c("invisible" = "black", "visible" = "#E69F00"), name = "Visibility") +
  scale_fill_manual(values = c("invisible" = "grey20", "visible" = "#E69F00"), name = "Visibility") +
  
  labs(
    title = "Cross-Experiment Continuous Moderation",
    subtitle = "Does the Baseline Shift strategy predict outcomes similarly across motion axes?",
    x = "Baseline Shift (px) [Independent ODD trials]",
    y = "Mean Forward Error (px) [Test trials]"
  ) +
  
  theme_classic(base_size = 12) +
  theme(
    strip.background = element_rect(fill = "grey95"),
    strip.text = element_text(face = "bold"),
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    legend.position = "bottom"
  )
```
